tstrait: a quantitative trait simulator for ancestral recombination graphs

### 2023-11-06 paper.tex
Rename
Line breaks

@@

\begin{figure}[!t]%
\centering
\includegraphics[width=213pt]{figure.png}
\caption{\textbf{Time taken to simulate quantitative traits.} Each point represents the mean time for 10 independent runs under different random seeds. The times reported are the total CPU time required to simulate quantitative traits on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM.
The trait model is a normal distribution with $\mu=0$, $\sigma^2=1$, $h^2=0.3$, and $\alpha=-1$. (A) Computational time with increasing number of individuals. The whole genome dataset from \emph{Homo sapiens} with various number of individuals and chromosome length are simulated by using \texttt{stdpopsim} \citep{adrion2020}. For each replicate of the simulation, \texttt{tstrait} is used to simulate one quantitative trait with 1000 causal sites. (B) Computational time with increasing number of causal sites on two large realistic ARGs. \texttt{tstrait} is used to simulate quantitative traits from the simulated French Canadian dataset \citep{anderson2023} and the inferred tree sequence dataset of the 1000 Genomes Project \citep{kelleher2019} with varying number of causal sites. The French Canadian dataset is downloaded from \url{https://zenodo.org/record/6839683}, and the inferred ARG from the 1000 Genomes Project is downloaded from \url{https://zenodo.org/record/3051855}. Chromosome 9 is selected for both datasets.}\label{fig:time}
\end{figure}

@@

%USE THE BELOW OPTIONS IN CASE YOU NEED AUTHOR YEAR FORMAT.
\bibliographystyle{abbrvnat}
\bibliography{reference}

>>>>

\usepackage{graphicx}

@@

\begin{figure}[!t]%
\centering
\includegraphics[width=213pt]{figure.pdf}
\caption{\textbf{Time taken to simulate quantitative traits.} Each point
represents the mean time for 10 independent runs under different random seeds.
The times reported are the total CPU time required to simulate quantitative
traits on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM. The trait model
is a normal distribution with $\mu=0$, $\sigma^2=1$, $h^2=0.3$, and
$\alpha=-1$. (A) Computational time with increasing number of individuals. The
whole genome dataset from \emph{Homo sapiens} with various number of
individuals and chromosome length are simulated by using \texttt{stdpopsim}
\citep{adrion2020}. For each replicate of the simulation, \texttt{tstrait} is
used to simulate one quantitative trait with 1000 causal sites. (B)
Computational time with increasing number of causal sites on two large
realistic ARGs. \texttt{tstrait} is used to simulate quantitative traits from
the simulated French Canadian dataset \citep{anderson2023} and the inferred
tree sequence dataset of the 1000 Genomes Project \citep{kelleher2019} with
varying number of causal sites. The French Canadian dataset is downloaded from
\url{https://zenodo.org/record/6839683}, and the inferred ARG from the 1000
Genomes Project is downloaded from \url{https://zenodo.org/record/3051855}.
Chromosome 9 is selected for both datasets.}\label{fig:time}
\end{figure}

@@

%USE THE BELOW OPTIONS IN CASE YOU NEED AUTHOR YEAR FORMAT.
\bibliographystyle{abbrvnat}
\bibliography{paper}
